---
title: "One-Way ANOVA"
output: github_document
---

## Introduction

The hypotheses of one way ANOVA are as follows:
$H_0 : \mu_1 =\mu_2 = \mu_3 $
$H_1 : \mu_1 \neq \mu_2 ~or~ \mu_2 \neq \mu_3~or~ \mu_3 \neq \mu_1 $

Basically we are going to test the weight differences among the positions in MLB. We chose 5 teams's 25 active roster data from mlb.com. To perform the analysis, we need to reshape the dataset form the wide to the long form.

```{r}
library(multcomp) # Multiple Comparisons Package
library(dplyr) #Reshaping data
mlbw = read.csv("mlbw.csv")
id <- rownames(mlbw)
mlbw <- cbind(id=id, mlbw)
mlbl = reshape(data=mlbw, idvar="id",
               varying = c("Pitchers","Infielder","Outfielder"),
               v.name=c("wt"),
               times=c("Pitchers","Infielder","Outfielder"),
               new.row.names = 1:1000,
               direction="long")
mlb<-na.omit(mlbl)
mlb <- mlb %>% rename(pos = time)
mlb$pos = as.factor(mlb$pos)
```

```{r mlb1}
boxplot(wt~pos, data=mlb)

out=lm(wt~pos, data=mlb)
anova(out)
par(mfrow=c(2,2))
plot(out)
shapiro.test(resid(out))

dunnett = glht(out, linfct= mcp(pos = "Dunnett"))
tukey = glht(out, linfct= mcp(pos = "Tukey"))
summary(dunnett)
summary(tukey)
par(mfrow=c(2,1))
plot(dunnett)
plot(tukey)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
