---
title: "Logistic Regression"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Odds ratio

An odds ratio is a measure of relationship between a certain factor A and a second factor B in a population. Specifically, it shows you how the presence of factor A has an effect on the presence of factor B. It is also used to figure out whether a particular exposure is a risk factor for a particular outcome, and to compare the various risk factors for that outcome.

## Logistic Regression

The logistic regression has a formula as follows: 

$ log \frac{p}{1-p}=\beta X. $

So you need to transformation to get the estimated odds ratio by taking $e$ to the coefficient.

## Example 1

The data comes from "Radelet, M. L. Racial Characteristics and the Imposition of the Death Penalty. American Sociological Review, v46 n6 p918-27 Dec 1981"

```{r}
death=read.csv("data/death_penalty.csv")
def=xtabs(count ~defendant+death, data=death)
chisq.test(def)
vic=xtabs(count ~victim+death, data=death)
chisq.test(vic)

out1=glm(death~victim*defendant,weights=count,family=binomial,data=death)
summary(out1)
out2=glm(death~victim,weights=count,family=binomial,data=death)
summary(out2)
anova(out2,out1,test="Chisq")
exp(coef(out2)["victimWhite"])
```

## Example 2


```{r}
library(MASS)
model=glm(low ~ lwt+factor(race)+smoke+ht+ui,data=birthwt, family=binomial)
summary(model)
exp(coef(model))
```
