---
title: "Nonlinear Regression"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Pharmacokinetics

One of the most important study that applys the nonlinear regression is Pharmacokinetics. It is the study about the absorption, distribution, digestion, and discharge of the drugs.

## One Compartment Model

The basic model is as follows:
$ C_t = C_0 e^{-Kt}. $

When you take a drug, the blood concentration has the maximum value as, $ C_0 $ and then exponentilaly decreases as time, t, goes. The elimination rate is K.

```{r one}
library("investr")
onecomp=read.csv("data/one_comp.csv")
one=nls(conc~C0*exp(-K*time),start=list(C0=41.3,K=0.64),data=onecomp)
summary(one)
plotFit(one)
```

## Two Compartment Model 

This model is adding one more term in addition to the previous model.
$ C_t = A_1 e^{-\beta_1 t} + A_2 e^{-\beta_2 t}.$ 

```{r two}
twocomp=read.csv("data/two_comp.csv")
two=nls(conc~SSbiexp(time, A1, lrc1, A2, lrc2), data=twocomp)
summary(two)
plotFit(two)
```

## One Compartment Model : Oral Dosage 

This model shows the blood concentration when the drug is taken by oral dosage.
$ C_t = \frac{D k_a k_e}{Cl(k_a + k_e)}(e^{-k_e t} + e^{-k_a t}).$ 

```{r oral}
oraldose=read.csv("data/oral_dose.csv")
oral=nls(conc~SSfol(Dose=4.4, time, lKe, lKa, lCl), data=oraldose)
summary(oral)
plotFit(oral, xlim=c(0,35))
```

## Michaelis-Menten Model

$ v= \frac{V_m x}{K+x}.$ 

```{r MM}
mime=read.csv("data/MM.csv")
mm=nls(rate~SSmicmen(conc,Vm,K), data=mime)
summary(mm)
plotFit(mm, ylim=c(0,130), xlim=c(0,400))
```
