---
title: "Tables"
output: github_document
---

## Fisher's Exact Test

The story of Fisher's exact test are as follows:
"Ronald Fisher, a Bad Cup of Tea, and the Birth of Modern Statistics", [https://www.sciencehistory.org/distillations/ronald-fisher-a-bad-cup-of-tea-and-the-birth-of-modern-statistics]

```{r}
teat=matrix(c(4,0,0,4), ncol=2)
fisher.test(teat)
chisq.test(teat)
```

As we can see the result, Dr. Bristol's ability is statistically significant with 5% critical level. Because of the number of observation, only 8 here makes a little gap between Fisher's exact test and Chi square test but they will converge on the same value as the sample size increases.

## Cochran-Armitage Trend Test

Sometimes we want to anaylyze the results as the intensity increases. However, the maximum intensity can bring some side-effect too. In this scenario, we would better use Chi square test as well to compare the results.



```{r}
prop.trend.test(c(13,10,10),c(42,14,28))
x=matrix(c(13,29,10,4,10,18), ncol=3)
chisq.test(x)
```

One thing we need to note is that when you use the trend test, we use the ratio between one dependent variable and the sum.